Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 evaluation.tex
Updated some of data with 1bn instruction runs.

We tested our system using all C benchmarks from SPECint
CPU2006 \cite{spec2006}. We focus on the C benchmarks because of our
modification of {\tt malloc} to support array bounds check. Although we do not
show results for the C++ benchmarks, we note that the results for UMC and DIFT
for these benchmarks are similar to the other results shown. For each
benchmark, we simulated for 200 million
instructions. An initial slack of 2 million cycles, which is less than 1\% of
the total execution time, is given for a 10\% target overhead. This initial
slack is scaled proportionally for other overhead targets.

\subsection{Baseline Monitoring Overheads}
% Full monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_full_mon.pdf}
    \vspace{-0.2in}
    \caption{Full monitoring overheads for UMC, BC, and DIFT.}
    \label{fig:evaluation.full_mon}
    \vspace{-0.1in}
  \end{center}
\end{figure} Figure~\ref{fig:evaluation.full_mon} shows the execution times of
performing full monitoring normalized to the execution times of the benchmarks
without monitoring. In these results, no filtering or partial monitoring is
done. UMC shows normalized execution times from 5x to 11x with an average
of 8x. BC shows normalized execution times of 15-28x with an average of
22x while DIFT shows normalized execution times of 11x-17x with an average of
14x. One of the reasons for these high overheads is that our implementations of
these monitors dynamically allocate memory for new metadata. This can be an
expensive, multi-cycle operation. Statically allocating memory for metadata
will reduce the execution time but requires a large upfront memory footprint.

@@

% Full monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_filtering.pdf}
    \vspace{-0.2in}
    \caption{Monitoring overheads with filtering for UMC, BC, and DIFT.}
    \label{fig:evaluation.filtering}
    \vspace{-0.1in}
  \end{center}
\end{figure}

Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times of 4x on average with filtering. For BC, normalized execution
times drop from 21x down to 3x. This is not surprising since in the baseline
implementation all loads and stores needed to be monitored. However, with
filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 13\% overheads
on average. This is due to the fact that for our implementation of DIFT on SPEC
benchmarks, we mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications we would expect to see a less
filtering

@@

Although the overheads of DIFT are quite low after filtering, BC and UMC still
show significant overheads. In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for further reduced overheads.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. We measure monitoring
coverage monitoring check operations that are still performed as a percentage
of the total number of monitoring check operations. This number does not
include the number metadata update operations that are done and serves as a
better metric for the actual coverage of the security or reliability technique.
The overhead is measured as a percentage of the program without monitoring. An
unrestricted dropping policy is used here.

We see that by varying the overhead budget, the coverage achieved also varies.
Furthermore, with only a 50\% overhead budget, array bounds check still
achieves 87\% monitoring coverage on average. This overhead budget corresponds
to 26\% of the average overheads seen by BC after filtering. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing monitoring coverage without
introducing overheads. The second effect is that, although we aggressively
filter out monitoring events, there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring. We see that
with a 50\% overhead budget, UMC achieves 50\% monitoring coverage on average.
This overhead budget corresponds to only 15\% of the overheads seen by UMC
after filtering.

>>>>

We tested our system using all C benchmarks from SPECint
CPU2006 \cite{spec2006}. We focus on the C benchmarks because of our
modification of {\tt malloc} to support array bounds check. Although we do not
show results for the C++ benchmarks, we note that the results for UMC and DIFT
for these benchmarks are similar to the other results shown. For each
benchmark, we simulated for 1 billion instructions. An initial slack of 1
million cycles, which is less than 1\% of
the total execution time, is given for a 10\% target overhead. This initial
slack is scaled proportionally for other overhead targets.

\subsection{Baseline Monitoring Overheads}
% Full monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_full_mon.pdf}
    \vspace{-0.2in}
    \caption{Full monitoring overheads for UMC, BC, and DIFT.}
    \label{fig:evaluation.full_mon}
    \vspace{-0.1in}
  \end{center}
\end{figure} Figure~\ref{fig:evaluation.full_mon} shows the execution times of
performing full monitoring normalized to the execution times of the benchmarks
without monitoring. In these results, no filtering or partial monitoring is
done. UMC shows normalized execution times from 4x to 11x with an average
of 7x. BC shows normalized execution times of 9-28x with an average of
18x while DIFT shows normalized execution times of 6x-17x with an average of
11x. One of the reasons for these high overheads is that our implementations of
these monitors dynamically allocate memory for new metadata. This can be an
expensive, many-cycle operation. Statically allocating memory for metadata
will reduce the execution time but requires a large upfront memory footprint.

@@

% Full monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_filtering.pdf}
    \vspace{-0.2in}
    \caption{Monitoring overheads with filtering null metadata for UMC, BC, and DIFT.}
    \label{fig:evaluation.filtering}
    \vspace{-0.1in}
  \end{center}
\end{figure}

Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times 2-6x with an average of 4x with null metadata filtering. For BC, normalized execution
times drop from 18x down to 4x on average. The range of normalized execution
times for filtered BC is 1.1-17x. This is not surprising since in the baseline
implementation all loads and stores needed to be monitored. However, with
filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 13\% overheads
on average after filtering with a maximum of 42\%. This is due, in part, to the fact that
for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications, which have larger amounts in
untrusted input data, we would expect to see less filtering.

@@

Although the overheads of DIFT are quite low after filtering, BC and UMC still
show significant overheads. In this section, we evaluate the effectiveness of
using partial monitoring (in addition to filtering) to trade-off coverage for further reduced overheads.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. We measure monitoring
coverage monitoring check operations that are still performed as a percentage
of the total number of monitoring check operations. This number does not
include the number metadata update operations that are done and serves as a
better metric for the actual coverage of the security or reliability technique.
The overhead is measured as a percentage of total number of checks performed
with full monitoring. The results shown here are using an unrestricted dropping
policy.

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 50\% overhead budget, array bounds check still
achieves 83\% monitoring coverage on average. This overhead budget corresponds
to just 20\% of the average overheads seen by BC after filtering only. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing monitoring coverage without
introducing overheads. The second effect is that, although we aggressively
filter out monitoring events, there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring. We see that
with a 50\% overhead budget, UMC achieves 51\% monitoring coverage on average.
Again, this overhead budget corresponds to only 20\% of the overheads seen by UMC
with filtering only.
